Recovery of deleted deep sequencing data sheds more light on the early Wuhan SARS-CoV-2 epidemic

### 2021-06-28 paper/paper.tex
update acknowledgements

\subsection{FASTQ files for SRR11313490 and SRR11313499}
I was not able to download SRA files for two runs, SRR11313490 and SRR11313499, from the Google Cloud.
After I posted the initial version of this pre-print, I was contacted by three different individuals (see Acknowledgments) who had uncovered FASTQ or FASTA files for these two missing runs that were downloaded from the SRA prior to the deletion of PRJNA612766.
For revised versions of the manuscript, I included analysis of the data for these two runs that I obtained from the links provided at \url{https://github.com/lifebit-ai/SARS-CoV-2/blob/master/assets/ucsc/aws_https_links.txt}.
Inclusion of data for these two runs did not appreciably change the results of the analysis relative to that in the original version of the pre-print, since both runs corresponded to low coverage samples for which meaningful viral genetic information could not be obtained.

@@

\section{Acknowledgments}
I thank the citizens and scientists on Twitter who helped inspire this study and inform its background through their analyses and discussions of the early spread of SARS-CoV-2.
I thank Brendan Larsen for pointing out that I failed to mask the primer binding site regions in the analysis described in the original pre-print (this has been fixed in this version).
I thank Andrew Fire (Stanford University), Theo Sanderson (Crick Institute), and Francisco de Asis de Ribera (DRASTIC Research) for finding locations of downloaded data for the two accessions (SRR11313490 and SRR11313499) that I could not download from the Google Cloud and so had to omit from the analysis described in the original pre-print (they are included in the analysis in this version).
I thank Stephen Goldstein and anonymous commenter for providing critiques of the original version of the pre-print on \textit{bioRxiv} that have helped me revise the manuscript.
I thank the scientists and labs who contributed sequences used in this study to the GISAID database; the names of these scientists and labs are listed in the tables linked to in the Methods.
The scientific computing infrastructure used in this work was supported by the NIH Office of Research Infrastructure Programs under S10OD028685.
The author is an Investigator of the Howard Hughes Medical Institute.

>>>>

\subsection{FASTQ files for SRR11313490 and SRR11313499}
I was not able to download SRA files for two runs, SRR11313490 and SRR11313499, from the Google Cloud.
After I posted the initial version of this pre-print, I was contacted by three different individuals who had uncovered FASTQ or FASTA files for these two missing runs that were downloaded from the SRA prior to the deletion of PRJNA612766.
For revised versions of the manuscript, I included analysis of the data for these two runs that I obtained from the links provided at \url{https://github.com/lifebit-ai/SARS-CoV-2/blob/master/assets/ucsc/aws_https_links.txt}.
Inclusion of data for these two runs did not appreciably change the results of the analysis relative to that in the original version of the pre-print, since both runs corresponded to low coverage samples for which meaningful viral genetic information could not be obtained.

@@

\section{Acknowledgments}
I thank the citizens and scientists on Twitter who helped inspire this study and inform its background through their analyses and discussions of the early spread of SARS-CoV-2.
I thank Brendan Larsen for pointing out that I failed to mask the primer binding site regions in the analysis described in the original pre-print (this has been fixed in this version).
I thank Stephen Goldstein and anonymous commenter for providing critiques of the original version of the pre-print on \textit{bioRxiv} that have helped me revise the manuscript.
I thank the scientists and labs who contributed sequences used in this study to the GISAID database; the names of these scientists and labs are listed in the tables linked to in the Methods.
The scientific computing infrastructure used in this work was supported by the NIH Office of Research Infrastructure Programs under S10OD028685.
The author is an Investigator of the Howard Hughes Medical Institute.
